### 2018-06-13 manuscript.tex
Autocommit (fgc)
Update manuscript.tex

There are at least three main theoretical perspectives from outside the communities
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  conventional theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.

@@

===============================

@@

%Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics \cite{BrowBeec13}.

>>>>

There are at least three main theoretical perspectives from outside the communities
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
+ \cite{Shel-Wand11}

@@

===============================
Concerns:

We did not consider ages of women's daughters.  For those whose daufhter is over 15(?), they were not likely to fgc them, but it doesnt' mean they are againt fgc.  It might just mean the daughters were too old to be fgced. 
===============================

@@

%Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics \cite{BrowBeec13}. 
 \cite{Shel-Wand11}:  supporting Mackie's convetion theory "expections regarding fgc are interdependent...."
